Peter Han Individual Report Edit

### 2020-04-14 doc/550/s550 report.tex
Final tweaking for submission. -gd

\bibliography{RealEstate.bib}

@@

\citet{s450-report} use the same dataset and offer a thorough description of the data in their analysis. In this report, however, all B.C. municipalities are included in analysis. The variables are summarised in Table \ref{table:variables}.  Missing mill rate values were imputed by using the average mill rate given by the data for the corresponding year and tax class code.

@@

@@

@@

@@

% Pick one of the two
The random forest (RF) algorithm is an ensemble learning method for classification and regression that operates by constructing numerous decision trees and choosing the majority class output (classification) or the average prediction (regression) given by the individual decision trees. Decision trees are trained on different samples (with replacement) of the data, and only a random subset of the covariates is used to define the split at each node, based on a recursive partitioning strategy. RF is preferred over a single decision tree as it overcomes the problem of over-fitting.

@@

@@

@@

@@

The main limitation of our analysis lies in the fact that the models assume independence of the data. However, as was argued in Section \ref{sec:data}, mill rates and assessment values are highly dependent on spatial information. An attempt to obtain the properties' spatial information was made by transforming the addresses into spatial coordinates using an open source geocoding system provided by the British Columbia Government. However, the open source geocoding system did not recognize some of the addresses in the dataset and provided incorrect coordinates for a large number of properties.  Therefore it is recommended that (1) addresses be formatted according to the standards required by the B.C. government, or (2) a private geocoding system that may be able to find addresses using the current format in the data is used. Provided spatial information is available, several model alternatives (e.g. factor models) could be tested to improve prediction accuracy, which take spatial information into account.

%%%% appendix
\printbibliography

>>>>

\bibliography{../../ref/RealEstate.bib}

@@

\citet{s450-report} use the same dataset and offer a thorough description of the data in their analysis. In this report, however, all B.C. municipalities are included in analysis. The variables are summarised in Table \ref{table:variables}.  Missing mill rate values were imputed by using the average municipality mill rate for the corresponding year and tax class code. This is sensible because mill rates are constant across municipalities, and so a more complex imputation technique is not necessary.

@@

\begin{table}[ht]
\centering
\rowcolors{2}{gray!20}{white}
\begin{tabular}{ll}
\rowcolor{gray!40}
\textbf{Variable}                & \textbf{Type}               \\ \hline
Mill rate                                                              & Continuous         \\
Total assessment                                                       & Continuous         \\
Total land assessment                                                  & Continuous         \\
Total improvement assessment & Continuous         \\
Tax class code                                                         & \begin{tabular}[c]{@{}l@{}}Categorical. \\ One of 1 (residential), 5 (industrial), 6 (commercial)\end{tabular}       \\
Municipality                                                           & Categorical        \\
Year & \begin{tabular}[c]{@{}l@{}}Discrete. \\ Values of 2016, 2017, 2018, and 2019\end{tabular} 
\end{tabular}
\caption{Brief description of the variables included in the data set.}
\label{table:variables}
\end{table}

@@

\begin{figure}[ht]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\textwidth]{figures/1. scatter with year.pdf}
  \caption{Scatterplot with year in different colors.}
  \label{fig:scatter_year}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\textwidth]{figures/2. scatter 2020 by municipality.pdf}
  \caption{Scatterplot only for 2020.}
  \label{fig:scatter_2020}
\end{subfigure}
\caption{Average log assessment values against log mill rates by municipality across the three different tax classes of interest.}
\label{fig:scatter}
\end{figure}

%\begin{figure}
%    \centering
%    \includegraphics[scale=0.55]{figures/1. scatter with year.pdf}
%    \caption{Log assessment values against log mill rates across the three different tax classes of interest, with year in different colors.}
%    \label{fig:scatter_year}
%\end{figure}

@@

\begin{figure}[ht]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\textwidth]{figures/6. mill rate evolution sample.pdf}
  \caption{Evolution of (log) mill rates.}
  \label{fig:evolution_millrate}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\textwidth]{figures/6.1 assessment evolution sample.pdf}
  \caption{Evolution of (log) assessment values.}
  \label{fig:evolution_assessment}
\end{subfigure}
\caption{Evolution of target variables over the years for some randomly-selected properties.}
\label{fig:evolution}
\end{figure}

%\begin{figure}[ht]
%    \centering
%    \includegraphics[scale=0.45]{figures/6. mill rate evolution sample.pdf}
%    \caption{Evolution of (log) mill rates over the years for some randomly-selected properties.}
%    \label{fig:rates_by_year}
%\end{figure}

\begin{figure}[ht]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\textwidth]{figures/7. violin mill rates.pdf}
  \caption{Distribution of (log) mill rates.}
  \label{fig:violin_millrate}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\textwidth]{figures/7.1 violin assessment values.pdf}
  \caption{Distribution of (log) assessment values.}
  \label{fig:violin_assessment}
\end{subfigure}
\caption{Violin and boxplots of (log) mill rates and (log) assessment values of individual properties across the three tax classes of interest, taking into account only the year 2020.}
\label{fig:violin}
\end{figure}

%\begin{figure}[ht]
%    \centering
%    \includegraphics[scale=0.45]{figures/7. violin mill rates.pdf}
%    \caption{Violin and boxplots of (log) mill rates of individual properties across the three tax classes of interest, taking into account only the year 2020.}
%    \label{fig:violin}
%\end{figure}

@@

% Pick one of the two
The random forest (RF) algorithm is an ensemble learning method for classification and regression that operates by constructing numerous decision trees and choosing the majority class output (classification) or the average prediction (regression) given by the individual decision trees. Decision trees are trained on different samples (with replacement) of the data, and only a random subset of the covariates is used to define the split at each node, based on a recursive partitioning strategy. RF is preferred over a single decision tree as it overcomes the problem of over-fitting.  The following models were constructed using the 'randomForest' package in R \citep{rfpack}.

@@

\begin{figure}[ht]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\textwidth]{figures/nodepur.png}
  \caption{Variable importance plot for mill rates.}
  \label{fig:4a}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\textwidth]{figures/asnodepur.png}
  \caption{Variable importance plot for assessment values.}
  \label{fig:4b}
\end{subfigure}
\caption{Variable importance plot based on increase in node purity for mill rate and total assessment value predictions.}
\label{fig:4}
\end{figure}

@@

% Bagging (aggregate bootstrap) was implemented by the random forest algorithm and performance is shown in Figure \ref{fig:5}. Bagging uses bootstrapping---sampling the data with replacement---and aggregation---combining several model predictions to obtain the best prediction.  The accuracy of predicting mill rates is less optimal for higher mill rates.  However, overall, the prediction power of the random forest models are desirable, particularly for predicting next year's assessment value.

\begin{figure}[ht]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\textwidth]{figures/bagmi.png}
  \caption{Performance for mill rates prediction.}
  \label{fig:5a}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\textwidth]{figures/bagas.png}
  \caption{Performance for assessment value prediction.}
  \label{fig:5b}
\end{subfigure}
\caption{Models' performance on test set.}
\label{fig:5}
\end{figure}
\FloatBarrier

@@

\begin{figure}[ht]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\textwidth]{figures/lmemill.png}
  \caption{Summary output for predicting mill rates.}
  \label{fig:6a}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\textwidth]{figures/lmeas.png}
  \caption{Summary output for predicting assessment values.}
  \label{fig:6b}
\end{subfigure}
\caption{Models summary output.}
\label{fig:6}
\end{figure}

\begin{figure}[ht]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\textwidth]{figures/diagmill.png}
  \caption{Diagnostics plots for LME model for mill rate.}
  \label{fig:7a}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\textwidth]{figures/diagas.png}
  \caption{Diagnostics plots for LME model for assessment values.}
  \label{fig:7b}
\end{subfigure}
\caption{Diagnostics plots.}
\label{fig:7}
\end{figure}

@@

The main limitation of our analysis lies in the fact that the models assume independence of the data. However, as was argued in Section \ref{sec:data}, mill rates and assessment values are highly dependent on spatial information. An attempt to obtain the properties' spatial information was made by transforming the addresses into spatial coordinates using an open source geocoding system provided by the British Columbia Government (see the documentation of \citet{geopy}). However, the open source geocoding system did not recognize some of the addresses in the dataset and provided incorrect coordinates for a large number of properties.  Therefore it is recommended that (1) addresses be formatted according to the standards required by the B.C. government, or (2) a private geocoding system that may be able to find addresses using the current format in the data is used. Provided spatial information is available, several model alternatives (e.g. factor models) could be tested to improve prediction accuracy, which take spatial information into account.

%%%% appendix and bibliography
\newpage
\printbibliography
